---
title: "Task1"
author: "Oleksandra Ustymenko"
date: "10/01/2024"
format:
  html:
    embed-resources: true
editor: source
---

## Question 1 title

Question description

```{r}
# code for solving task 
v1 <- 10.62636237
v2 <- 40L
v3 <- "character variable skjdhfkjshadfjksdhf"
v4 <- TRUE
v5 <- 16+8i 
print(c(v1, v2, v3, v4, v5))
```



## Question 2 

Question description

```{r}
# code for solving task
sequence_vector <- 5:25
number_vector <-  c(3.14, 2.71, 0.13)
true_vector <- rep(TRUE,100)
```
## Question 3
Question description
Create the next matrix:

|  |   |  |
|:---:|:-----:|:---:|
| 12  | 34    | 87  |
| -12 | -12.1 | 0   |
| 3.6 | 0.5   | 1.3 |
```{r}
# code for solving task
my_data <-  matrix(c(12,34,87,-12,12.1, 0, 3.6, 0.5, 1.3), nrow= 3, byrow= TRUE)
print (my_data)
```

## Question 4
Question description :
Create a `list` with all atomic types.
```{r}
# code for solving task
my_list <-  list(
  integer_value = 66L,
  numeric_value= 4.573353,
  character_value= "shvushvvshvhdbdh",
  logical_value= TRUE,
  complex_value= 16+8i
)
my_list 
```
## Question 5
Question description :
Create a `factor` with 3 levels: `infant`, `child`, `adult`.
```{r}
# code for solving task
my_factor <- factor(c("big", "avarage" , "small", "small", "avarage", "big"),
levels= c("big", "avarage" , "small"))
my_factor
```


## Question 6
Question description :
Create a `data frame`
```{r}
# code for solving task
age_factor <-factor(c("infant", "child", "adult"), levels= c("infant","child", "adult"))

print(age_factor)
```

## Question 7
Question description :
Change column names of the `data frame`.
```{r}
# Example Data Frame
df <- data.frame(
  Column1 = c(1, 2, 3),
  Column2 = c(4, 5, 6),
  Column3 = c(7, 8, 9)
)

# Print the original data frame
print("Original Data Frame:")
print(df)

# Changing the column names
colnames(df) <- c("NewName1", "NewName2", "NewName3")

# Print the updated data frame
print("Updated Data Frame with New Column Names:")
print(df)
```



