---
title: "Task2"
author: "Oleksandra Ustymenko"
date: "10/01/2024"
format:
  html:
    embed-resources: true
editor: source
---

## Question 1 
Question description
Create the next random vector:

```{r message=FALSE}
v <- rnorm(50)
```

For the vector print:

- 10th item,
- items from 10th to 20th (including 20th item),
- 10 items starting from 5th,
- all items bigger than 0,
- last 5 items

```{r}
# code for solving task 
# Generate a random vector of 50 elements
v <- rnorm(50)

# Print the 10th item
v[10]

# Print items from 10th to 20th (including the 20th item)
v[10:20]

# Print 10 items starting from the 5th
v[5:(5+9)]

# Print all items bigger than 0
v[v > 0]

# Print the last 5 items
v[(length(v)-4):length(v)]
```
## Question 2
Question description
Create the next data frame:

```{r message=FALSE}
df <- 
  data.frame(a = rnorm(50), b = 1:50, 
             cc = sample(letters, 50, replace = TRUE))

```

For the data frame find and print:

- the last 10 rows,
- 15th item of columns `cc`,
- subset columns `a` and `b` and rows from 10th to 20th (including 20th),
- a new vector from column `b`.
```{r}
# code for solving task 
# Create the data frame
df <- data.frame(a = rnorm(50), b = 1:50, cc = sample(letters, 50, replace = TRUE))

# Print the last 10 rows
tail(df, 10)

# Print the 15th item of column 'cc'
df$cc[15]

# Subset columns 'a' and 'b', and rows from 10th to 20th (including 20th)
df[10:20, c("a", "b")]

# Create a new vector from column 'b'
new_vector_b <- df$b
new_vector_b
```
## Question 3
Question description
Create the next random vector:

```{r}
v_na <- rnorm(30)
num_na <- sample(10, 1)
v_na[sample(30, num_na)] <- NA
```

For this vector:

- print all not NA items,
- find how many NA values the vector has,
- find `min` `max` and `mean` for the vector.
```{r}
# code for solving task 
# Create the random vector
set.seed(123)  # Set seed for reproducibility (optional)
v_na <- rnorm(30)          # Generate 30 random values from a normal distribution
num_na <- sample(10, 1)    # Randomly select the number of NA values
v_na[sample(30, num_na)] <- NA  # Assign NA to random positions in the vector

# 1. Print all non-NA items
non_na_items <- v_na[!is.na(v_na)]
print("Non-NA items in the vector:")
print(non_na_items)

# 2. Find how many NA values the vector has
num_na_values <- sum(is.na(v_na))
print(paste("Number of NA values in the vector:", num_na_values))

# 3. Find the minimum, maximum, and mean of the vector (excluding NA values)
min_value <- min(v_na, na.rm = TRUE)
max_value <- max(v_na, na.rm = TRUE)
mean_value <- mean(v_na, na.rm = TRUE)

print(paste("Minimum value (excluding NA):", min_value))
print(paste("Maximum value (excluding NA):", max_value))
print(paste("Mean value (excluding NA):", mean_value))



```






